%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{\textbf{Senior Software Engineer, Infra}} % Job title
	{Databricks} % Organisation
	{Remote, United Kingdom} % Location
	{Apr 2025 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item{Started as a Senior Site Reliability Engineer
						at Neon.tech, that got acquired by Databricks family, where we are bridging the gap between
						analytical, transactional database systems.}
			\item {The SRE Team is responsible for managing Neon’s multi-region, multi-cloud deployment in close
			            collaboration with the broader engineering team, as well as improving the reliability of the overall
			            platform. All the features we want to implement can only reach our customers if the changes are
			            delivered in a reliable way, which means the SRE team plays a significant role in defining our pace of
			            development.}
			\item {\textbf{Technical Skills:} Go, Linux, PostgreSQL, Kubernetes, Distributed Systems, Database Infra}
		\end{cvitems}
	}

	\cventry
	{\textbf{Career Break}} % Job title
	{Career Break} % Organisation
	{United Kingdom} % Location
	{Sep 2024 - Apr 2025} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Time dedicated to family and personal care.}
		\end{cvitems}
	}

	\cventry
	{\textbf{Production Engineer}} % Job title
	{Meta / Facebook} % Organisation
	{London, United Kingdom} % Location
	{Mar 2022 - Aug 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Member of the Backup and Restore team, building services and tooling ensuring the ability to recover data
			            from backups for both the MySQL and ZippyDB (main key/value store at Meta) reliably, efficiently and
			            correctly, serving as the defence line against data loss and corruption across all our family of
			            services and apps (Facebook, Messenger, Instagram, and WhatsApp, serving 3.7 Billion users). MySQL at
			            Meta is one of the largest -if not the largest- installations on the planet.}
			\item {Focused on the recovery area, leading and implementing projects ensuring and unblocking our ability to
			            restore huge amounts of data in disaster scenarios, and projects that reduce RTO (Restore Time
			            Objective) for the datastores we support.}
			\item {Participated in and influence roadmapping sessions and team prioritisation efforts, building shared
			            consensus, listening to feedback, and deriving insights from production issues, insights, and toil to
			            ensure we are always working on the most important projects.}
			\item {Participated in oncall rotation, leading investigations into incidents related to our services, as well as
			            helping other teams recover from incidents in their tech stacks with backups of their data (including
			            high visibility SEVs and incidents).}
			\item {Identified performance bottlenecks in backup and restore agents running fleet wide, and implemented fixes
			            reducing the memory and compute footprint of those agents running on hundreds of thousands of serves.}
			\item {Lead many investigations into production issues and incidents, ensuring they are mitigated, root-caused, and
			            have the proper follow up actions that are properly assigned to owners and tracked their progress
			            until they are resolved.}
			\item {Improved investigation practices and introduced new best practices (that were adopted by our team and other
			            teams in the org), and continuously improved team's monitoring dashboards and alert suite to surface
			            issues that were not visible enough, incorporating data points from investigations and incidents.}
			\item {Designed and implemented integration with new services and platforms at Meta that our services depend on
			            (e.g. storage services for backups).}
			\item {Lead and participated in multiple decommissioning projects for services that impact all team at Meta
			            ensuring they are decommissioned responsibly and reliably.}
			\item {Mentored juniors on the team, and onboarded new team members to our stack, practices and culture, ensuring
			            they have all the context they need to succeed, as well as unblocking them and helping them be
			            successful in their role in the team and the company.}
			\item {Production Engineering at Meta combines software, systems, and infra engineering. Production Engineers are
			            known for their ability to work on a wide variety of projects across multiple teams supporting the 3.7
			            billions users of our platforms.}
			\item {\textbf{Technical Skills:} Python, Rust, Golang, Linux, MySQL, ZippyDB, Distributed Systems, Database Infra,
			            Thrift, Mercurial}
		\end{cvitems}
	}

	\cventry
	{\textbf{Senior Site Reliability Engineer}} % Job title
	{Twitter} % Organisation
	{London, United Kingdom} % Location
	{May 2020 - Mar 2022} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Member of Twitter's Database SRE team providing entire company with Database infra, mainly MySQL clusters
			            (both dedicated, and multi-tenant), in addition to PostgreSQL, Vertica, and Druid clusters).}
			\item {Designed and built a service that automates toil in the team. The service resulted in a 98\% drop in "time
			            to provision resources", that is more than 100k person-hours worth of savings (i.e. >139 person
			            months, >11.5 person years) in the next few years.}
			\item {Monitored and improved availability, scalability, performance and reliability of services owned by our
			            team.}
			\item {Participated in the team's oncall rotation, ensuring production issues and incidents are uncovered and
			            addressed properly.}
			\item {Lead projects to reduce oncall noise, and authored runbooks and documentation improving the team's incident
			            response posture.}
			\item {Mentored and onboarded new team members to the team, the tech stack, and helped them become effective and
			            successful members on the team.}
			\item {\textbf{Technical Skills:} Python, Flask, SQLAlchemy, Linux, MySQL, PostgreSQL, Vertica, Druid, Apache
			            Mesos, Apache Aurora, Git}
		\end{cvitems}
	}

	\cventry
	{\textbf{Site Reliability Engineer}} % Job title
	{GoCardless} % Organisation
	{London, United Kingdom} % Location
	{Mar 2019 - Mar 2020} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Protect, provide for, and progress the software and systems that make up the GoCardless product, supporting
			            product teams in the deployment of high quality services.}
			\item {\textbf{Technical Skills:} Golang, PostgreSQL, GCP, Kubernetes, Terraform, Helm, Elastic Search, Kibana,
			            Linux, Docker, Git, Prometheus, Grafana, Thanos}
		\end{cvitems}
	}

	\cventry
	{\textbf{Software Engineer}} % Job title
	{WeQ Global Tech GmbH} % Organisation
	{Berlin - Germany} % Location
	{Nov 2017 - Mar 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Developed, deployed \& maintained customer facing services handling billions of requests per day.}
			\item {Created and maintained infrastructure as code for both new and legacy systems/microservices.}
			\item {Implemented autoscaling and self healing features into new services.}
			\item {\textbf{Technical Skills:} PHP, Java, Spring Boot, Vert.x, Kafka, Linux, MySQL, MongoDB, AWS, Docker,
			            Docker Swarm, Terraform, Vagrant, Jenkins, Prometheus, Grafana}
		\end{cvitems}
	}

	\cventry
	{\textbf{Sr. Software \& Platform Engineer - Tech Lead}} % Job title
	{Levelset (formerly zlabs, acquired by Procore)} % Organisation
	{Cairo - Egypt} % Location
	{Mar 2013 - Oct 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Lead the team in designing \& developing an internal platform for data verification and research process.}
			\item {Lead the migration of the levelset.com platform to a microservices based architecture, and mentored the
			            team throughout the process.}
			\item {Designed \& built the API that enabled Levelset to onboard enterprise customers by bulk importing their
			            projects into the platform.}
			\item {Worked with enterprise customers to integrate their systems with our API and provided them with the support
			            they needed to successfully onboard to the platform.}
			\item {Designed and built the PDF generation engine that generated legal/financial letters for all our customers
			            to secure their lien rights. This is the core feature of the platform.}
			\item {Designed \& and lead building various growth products/features that acquired new customer segments.}
			\item {\textbf{Technical Skills:} PHP, Symfony, Linux, MySQL, Neo4j, AWS, RabbitMQ, Apache Web Server, Soap API,
			            Rest API, Jenkins, Git, Nagios, New Relic}
		\end{cvitems}
	}

	\cventry
	{\textbf{Senior Software Engineer, DevOps}} % Job title
	{} % Organisation
	{} % Location
	{Mar 2013 - Oct 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Overhauled, stabilised and scaled the MySQL backing infrastructure.}
			\item {Designed the new cloud infrastructure (AWS), built automation tools and established system monitoring,
			            performance measurements, and fully automated deployments}
			\item {Migrated the platform from single point of failure virtual private servers (Slicehost) to the cloud (AWS).}
			\item {Worked closely with engineers and business folks to identify and solve operational and customer issues with
			            our services, tools and apps.}
			\item {Optimised time to release by orders of magnitudes (from 2 days to an average of 3-5 minutes), and improved
			            uptime (99.99\% from several outages a week).}
			\item {Maintained and operated Git source repositories, defining branching strategies and tutoring the engineering
			            teams about it.}
			\item {\textbf{Technical Skills:} PHP, Symfony, Linux, MySQL, Neo4j,  AWS, RabbitMQ, Soap API, Rest API, Jenkins,
			            Apache Web Server, Git, Nagios, New Relic}
		\end{cvitems}
	}

	\cventry
	{\textbf{Senior Software Engineer}} % Job title
	{Handmade Studios} % Organisation
	{Cairo - Egypt} % Location
	{Jun 2012 - Feb 2013} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed, developed \& maintained an editorial website for entrepreneurs and startups.}
			\item {\textbf{Technical Skills:} PHP, Symfony, Linux, MySQL, MongoDB, AWS, Apache Web Server, Git}
		\end{cvitems}
	}

	\cventry
	{\textbf{Senior Software Engineer}} % Job title
	{Inmobly} % Organisation
	{Cairo - Egypt} % Location
	{Nov 2011 - May 2012} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed, developed \& deployed API backends for two mobile apps that recorded and streamed videos.}
			\item {\textbf{Technical Skills:} Python, Flask, SQLAlchemy, Rest, AWS, Subversion (svn)}
		\end{cvitems}
	}

	\cventry
	{\textbf{Technical Consultant}} % Job title
	{Bluw i LTD} % Organisation
	{Cairo - Egypt} % Location
	{Jun 2011 - Sep 2011} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented a social network for entrepreneurs to raise funds from angel investors.}
			\item {\textbf{Technical Skills:} PHP, Drupal, AWS, Apache Web Server, Git}
		\end{cvitems}
	}

	\cventry
	{\textbf{Software Engineer, Tech Lead}} % Job title
	{Wuzzuf.net} % Organisation
	{Cairo - Egypt} % Location
	{Apr 2010 - Apr 2011} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed the architecture and laid out the technical vision and guidelines for Wuzzuf.net, the leading
			            platform in Egypt and the Middle East.}
			\item {Worked with, guided, and mentored the team in executing the technical vision, and delivering Wuzzuf.net
			            from scratch.}
			\item {Worked closely with the CTO and CEO.}
			\item {Designed, created, monitored and maintained the infrastructure of Wuzzuf.net.}
			\item {\textbf{Technical Skills:} PHP, MySQL, AWS, Apache Web Server, Mercurial, CakePHP, Doctrine ORM, BitBucket}
		\end{cvitems}
	}

	\cventry
	{\textbf{Senior Software Engineer}} % Job title
	{Arabia Inform} % Organisation
	{Cairo - Egypt} % Location
	{Nov 2009 - Apr 2010} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed and built an in-house media archival and indexing solution with media encoding and advanced search
			            capabilities and features.}
			\item {Implemented and launched ads management infra and services for the company’s websites network.}
			\item {Mentored other teams on infra upgrade and migration projects.}
			\item {\textbf{Technical Skills:} PHP, Drupal, MySQL, Apache Web Server, OpenX, AWS, Git}
		\end{cvitems}
	}

	\cventry
	{\textbf{Software Engineer}} % Job title
	{Citex Software} % Organisation
	{Cairo - Egypt} % Location
	{Oct 2008 - Nov 2009} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented a social network for entrepreneurs to raise funds from angel investors.}
			\item {\textbf{Technical Skills:} PHP, Drupal, MySQL, AWS, Git, Apache Web Server, Nagios}
		\end{cvitems}
	}

	\cventry
	{\textbf{PHP Developer}} % Job title
	{Media International} % Organisation
	{Cairo - Egypt} % Location
	{Jan 2007 - Sep 2009} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed, developed, deployed various PHP projects for customers and maintained them in production ensuring
			            their availability.}
			\item {Lead various data migration projects for clients including, ensuring safe, correct, and efficient data
			            migration from legacy systems to the new solutions we implemented with minimal to no downtime.}
			\item {Created and maintained the "Tech Radar" for the org.}
			\item {Designed and implemented load balancing linux for web services.}
			\item {Designed and implemented MySQL architecture, including replication.}
			\item {Implemented a service to centralise file and object management solution for our services.}
			\item {Designed and implemented the monitoring strategies and infra for our services, and was heavily involved in
			            resolving production issues, and maintaining our services availability and uptime.}
			\item {\textbf{Technical Skills:} Linux, MySQL, PHP, Drupal, Joomla, Moodle, Apache Web Server, Nagios}
		\end{cvitems}
	}

	\cventry
	{\textbf{PHP Developer}} % Job title
	{20at.com} % Organisation
	{Cairo - Egypt} % Location
	{Jun 2004 - Dec 2006} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Designed and implemented a content management system (CMS) from scratch to meet the demands of editorial
			            and business requirements.}
			\item {Designed and executed data migration projects from the legacy systems of to the newly developed services
			            with minimal downtime.}
			\item {Maintained the online services and website and defined the strategies and tooling for bug fixing and
			            security patches.}
			\item {Developed and shipped features (including whole new sub-portals) to meet the business and editorial needs
			            for major and current events (e.g. a full new portals for reporting on Football World Cup 2006,
			            Presidential elections in Egypt, and some of the major conflicts in the area.).}
			\item {\textbf{Technical Skills:} PHP, Linux, MySQL, Linux, AWS, Apache Web Server, S/FTP}
		\end{cvitems}
	}
\end{cventries}
